High angular resolution dust density and temperature maps from \Herschel\ imaging data

### 2012-08-05 documents/herschel_dust.tex
small tweaks

In detail, this works by choosing a random integer $1\leq s\leq S$
(where $S$ is the number of leave-some-out trials, $S=8$ in what
follows) for every data pixel $n$.  For each value of $s$---say
3---MAP values for the dust-map parameters are obtained given all the
data \emph{except} that marked with integer $s=3$.  The data marked
with integer $s=3$ are predicted by this model, and a prediction
$\chi^2$ value is computed for the left-out $s=3$ data.  This is
repeated for all values of $s$ and all 8 prediction $\chi^2$ values
are summed.  This total prediction leave-some-out $\chi^2$ is a
function of the hyperparameters; the hyperparameters $\alpha$ at which
it is minimized are chosen as the best hyperparameters.

@@

...(in detail, sky)...

>>>>

In detail, this works by choosing a random integer $s$ with $1\leq
s\leq S$ (where $S$ is the number of leave-some-out trials, $S=8$ in
what follows) for every data pixel $n$.  For each value of $s$---say
3---MAP values for the dust-map parameters are obtained given all the
data \emph{except} that marked with integer $s=3$.  The data marked
with integer $s=3$ are predicted by this model, and a prediction
$\chi_s^2$ value is computed for the left-out $s=3$ data.  This is
repeated for all values of $s$ and all $S$ prediction $\chi_s^2$
values are summed.  This total prediction leave-some-out $\chi^2$ is a
function of the hyperparameters; the hyperparameters $\alpha$ at which
it is minimized are chosen as the best hyperparameters.

@@

...details of $\theta_k$, small patch, and so-on...

...(in detail, sky level)...

...what happened in the cross-validation...

...results and jackknifes...
